---
title: "Task Three (Sentence-Level Analysis)"
author: "Jiayue Lu"
data: 2021/12/08
output:
  pdf_document:
    df_print: paged
---

```{r setup, include=FALSE}
options(warn=-1)
knitr::opts_chunk$set(echo = TRUE)

# Required packages loading

library(tidytext)
library(gutenbergr)
library(tidyverse)
library(dplyr)
library(sentimentr)
library(ggplot2) 
```

```{r include=FALSE}
# Book ID for my selected book
book_id <- 1424

# Prepare the book data
book_data <- gutenberg_download(book_id)

# Merge all the text into a string.
book_str <- paste(book_data$text, sep = "")
```

```{r include=FALSE}
# Split the string into sentences with batch id
book_sentences <- book_str %>%
  get_sentences() %>%
  sentiment() %>%
  filter(!is.na(word_count)) %>%
  mutate(batch_id = row_number() %/% 25)
```

```{r include=FALSE}
# Classify polarity into three types of sentiment (positive, neutral and negative) and calculate the level of polarity
book_polarity <- book_sentences %>%
  mutate(polarity_level = ifelse(sentiment > 0.3, "positive", ifelse(sentiment < -0.3, "negative", "neutral"))) %>%
  count(batch_id, polarity_level) %>%
  spread(polarity_level, n, fill = 0) %>%
  mutate(polarity_level = positive - negative)
```


Refer to https://www.r-bloggers.com/2020/04/sentiment-analysis-in-r-with-sentimentr-that-handles-negation-valence-shifters/, I did a sentence-level sentiment analysis over my book (gutenberg_id = 1424).

The biggest difference between word-level sentiment analysis and sentence-level sentiment analysis is about the Negation words. For example, 

“I’m happy” -> Positive “I’m not happy” -> Negative.

In word-level sentiment analysis, it can only get "not" and "happy" separately and it will recognize it as positive sentiment. However, in sentence-level sentiment analysis, "not happy" will be analyzed in one sentence and get the negative sentiment instead.

The result of Task 2 and Task 3 are not the same due to the difference between word-level analysis and sentence-level analysis. But we can capture some obivious trend at some points, like 55. And also some fully inverse result like 137-150. The result proves that word-level analysis is more accurate at some low magnitude, while sentence-level analysis can capture the overall sentiment in a large unit. In the future, it will be great to conduct sentiment analysis by combining different levels of analysis (words, sentence, paragraph, character).



```{r echo=FALSE}
# Refer to book "Text Mining with R: A Tidy Approach"
# Generate the sentiment level distribution figure:
ggplot(book_polarity, aes(batch_id, polarity_level, fill = 1424)) +
  geom_col(show.legend = FALSE, aes(fill = "red")) +
  facet_wrap(~"Castle Rackrent", ncol = 1, scales = "free_x")
```

